---
title: "Homework_8"
author: "Maha Siva"
date: "2025-04-11"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(mosaic)
```

Github link: https://github.com/MahaSiva1/Homework_8

# Problem 1 
```{r, echo=FALSE}
creat <- read.csv("creatinine.csv")
```

### Part A 
```{r, echo=FALSE}
model_creat = lm(creatclear ~ age,data=creat)
coef(model_creat)
#147.8129158 - 0.6198159*55 equals 113.723

```

To estimate the creatinine clearance as a function of age a linear regression model by the equation 147.813 - .620 * age. In this context 147.813 is the intercept which is the creatinine clearance of someone with a size 0. -.62 is the slop which represents how much the creatinie changes per year. For a 55 year old we would use the equation 147.813 - .620 * 55 which would equal 113.723 mL/min. 

### Part B 
We know the slope of our regression model is -0.62. This signifies that for every additional year of age, the creatinine clearance rate will decreased on average by 0.62 mL/min.  

### Part C 

```{r, echo=FALSE}
147.8129158 - 0.6198159*40 
#123.0203

147.8129158 - 0.6198159*60
#110.624

```

The 40 year old has a healthier clearance rate. When we compute the expected values for the clearance rate for both of the individuals, we see that the 40 year old has a value of 123.02 and the 60 year old has a expected value of 110.624 mL/min.



When we subtract the difference between the expected and the actual the 40 year old has a difference of 11.9 mL/min. and the 60 year old has a difference 1.376 mL/min. The 40 year old has a greater difference which means they have a higher rate than expected which, in result, means they have a healthier clearance rate. 


# Problem 2:Modeling disease growth
```{r, echo=FALSE}
covid <- read.csv("covid.csv")
```

### Question 1 
```{r, echo=FALSE}
italy <- filter(covid, country == "Italy")
boot_italy = do(10000) * lm(log((deaths)) ~ (days_since_first_death), data=resample(italy))
confint(boot_italy, level = 0.95)

```
Our 95% confidence interval for the growth rate is [.160, .208]. Our doubling time is [4.38, 3.36].

### Question 2 
```{r, echo=FALSE}
spain <- filter(covid, country == "Spain")
boot_spain = do(10000) * lm(log((deaths)) ~ (days_since_first_death), data=resample(spain))
confint(boot_spain, level = 0.95)


```
Our 95% confidence interval for the growth rate is [.235, .31721]. Our doubling time is [2.97, 2.206]

### Question 3 
```{r, echo=FALSE, message=FALSE}
library(ggplot2)

ggplot(covid) + geom_line(aes(x=(days_since_first_death), y=log(deaths), color = country)) + labs(x="Days Since First Death", y="Deaths (log scale)", title="Days Since First Death vs. Deaths ")

```

# Problem 3
```{r, echo=FALSE}
milk <- read.csv("milk.csv")
#lm_milk <- lm(log(sales)~log(price), data=milk)
#boot_spain = do(10000) * lm(log((deaths)) ~ (days_since_first_death), data=resample(spain))

boot_milk = do(10000) * lm(log(sales)~log(price), data=resample(milk))
confint(boot_milk, level = .95)
```

The estimated price elasticity of demand for milk is -1.62 with a 95% bootstrapped confidence interval from [-1.77,-1.45]. This illustrates that as an average across milk, a 1% change in price produces a -1.62% change in milk sales, on average. 

The power-law model of this form was used which is Q = K * p^beta. Taking the log of both sides we get log(Q) = log(K) + beta * log(p). 

I then fit this new model using linear regression of log(sales) and bootstrapped the model 10,000 times to obtain a confidence interval for the elasticity estimate B. We know that the slope of this model will correlate to the price elasticity. In addition, since the confidence interval does not include 0, this result is statistically significant. 



